### 2020-12-19 paper/localpsf.tex
figured out clear proof for infinite dimensional weighting function theorem

In Algorithm \ref{alg:weighting_functions_incremental}, we show how to efficiently solve optimization problem \eqref{eq:wi_optimization_problem}, and thus compute $w_i$. We prove \ref{alg:weighting_functions_incremental} in Theorem \ref{thm:wi_alg_is_correct}. Constructing all $r$ of the functions $w_i$ requires solving the Poisson equation $2r$ times with different right hand side sources, and these Poisson PDE solves can be performed cheaply with multigrid. All the existing weighting functions, $\{w_i\}_{i=1}^r$, will change if a new point, $x_{r+1}$, is added. The Poisson PDE solves can be performed incrementally, so that we only need to perform two new Poisson PDE solves when a new point is added, rather than $2(r+1)$ new PDE solves.

@@

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to the Poisson problem
			\begin{equation*}
			\Delta \psi_i = \delta_{x_i}, \quad \text{in }\Omega,
			\end{equation*}
			with Neumann boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

			Compute $\theta_i$ as the solution to the Poisson problem
			\begin{equation*}
			\Delta \theta_i = \psi_i, \quad \text{in }\Omega,
			\end{equation*}
			with Neumann boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

@@

		Form the $r \times r$ matrix $S$ with entries
		$$S_{ij} = \left(\psi_i, \psi_j\right)_{L^2(\Omega)}.$$

@@

			Compute 
			\begin{equation*}
			\lambda = -S^{-1} \left(e_i - \alpha \mathbf{1} \right).
			\end{equation*}

			Form the weighting function $w_i$ given by
			$$w_i(x) = \alpha - \sum_{k=1}^r \lambda_k \theta_k(x).$$
		}
	}
	\caption{Compute weighting functions $w_i$, $i=1,\dots,r$.}
	\label{alg:weighting_functions_incremental}
\end{algorithm2e}

@@

>>>>

In Algorithm \ref{alg:weighting_functions_incremental}, we show how to efficiently solve optimization problem \eqref{eq:wi_optimization_problem}, and thus compute $w_i$. We prove correctness of Algorithm \ref{alg:weighting_functions_incremental} in Theorem \ref{thm:wi_alg_is_correct}. Constructing all $r$ of the functions $w_i$ requires solving the Poisson equation $2r$ times with different right hand side sources, and these Poisson PDE solves can be performed cheaply with multigrid. All the existing weighting functions, $\{w_i\}_{i=1}^r$, will change if a new point, $x_{r+1}$, is added. The Poisson PDE solves can be performed incrementally, so that we only need to perform two new Poisson PDE solves when a new point is added, rather than $2(r+1)$ new PDE solves.

@@

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to the Poisson problem
			\begin{equation}
			\label{eq:psi_eq}
			\Delta \psi_i = \delta_{x_i}, \quad \text{in }\Omega,
			\end{equation}
			with Neumann zero boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

			Compute $\theta_i$ as the solution to the Poisson problem
			\begin{equation}
			\label{eq:theta_eq}
			\Delta \theta_i = \psi_i, \quad \text{in }\Omega,
			\end{equation}
			with Neumann zero boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

@@

		Form the $r \times r$ matrix $S$ with entries
		\begin{equation}
		\label{eq:defn_of_S_alg}
		S_{ij} = \left(\psi_i, \psi_j\right)_{L^2(\Omega)}.
		\end{equation}

@@

			Compute 
			\begin{equation}
			\label{eq:definition_of_mu_alg}
			\lambda = -S^{-1} \left(e_i - \alpha \mathbf{1} \right).
			\end{equation}

			Form the weighting function $w_i$ given by
			\begin{equation}
			\label{eq:definition_of_wi_alg}
				w_i(x) = \alpha - \sum_{k=1}^r \lambda_k \theta_k(x).
			\end{equation}
		}
	}
	\caption{Compute weighting functions $w_i$, $i=1,\dots,r$.}
	\label{alg:weighting_functions_incremental}
\end{algorithm2e}

@@

\begin{proof}
	For notational convenience, in this proof we write $w$, $\lambda$, and $e$ instead of $w_i$, $\lambda_i$, and $e_i$, respectively. Here subscripts for $\lambda$, and $e$ instead denote components of those vectors. For example, here $\lambda_j$ denotes the $j^\text{th}$ component of the vector $\lambda$, which corresponds to the $j^\text{th}$ of the vector $\lambda_i$ in Algorithm \ref{alg:weighting_functions_incremental}.

	In this proof, we will repeatedly make use of the fact that
	\begin{equation}
	\label{eq:inline_wi_lemma}
	\left(\psi_j, \Delta h\right)_{L^2(\Omega)} = h(x_j)
	\end{equation}
	for all $h\in H^2_N(\Omega)$. This follows from integration by parts and the definition of $\psi$ in \eqref{eq:psi_eq}.

	From standard optimization theory, the solution to optimization problem \ref{eq:wi_optimization_problem} is the stationary point of the Lagrangian,
	\begin{equation*}
		\mathcal{L}(w,\lambda) = \frac{1}{2}\|\Delta w\|^2 + \sum_{j=1}^r \lambda_j\left(e_j - w(x_j)\right).
	\end{equation*}
	Using the definition of $w_i$ in \eqref{eq:definition_of_wi_alg}, we may write the gradient of $\mathcal{L}$ with respect to $\lambda_j$ as
	\begin{equation*}
		\nabla_{\lambda_j} \mathcal{L}(w, \lambda) = e_j - w(x_j) 
		= e_j - \alpha + \sum_{k=1}^r \lambda_k \theta_k(x_j).
	\end{equation*}
	Using \eqref{eq:inline_wi_lemma} with $h=\theta_k$, the equation for $\theta$ in \eqref{eq:theta_eq}, and the definition of $S$ in \eqref{eq:defn_of_S_alg}, we have
	\begin{align*}
		\sum_{k=1}^r \lambda_k \theta_k(x_j) &= \sum_{k=1}^r \lambda_k \left(\psi_j, \Delta \theta_k\right)_{L^2(\Omega)} \\
		&= \sum_{k=1}^r \lambda_k \left(\psi_j, \psi_k\right)_{L^2(\Omega)} = \left(S \lambda\right)_j.
	\end{align*}
	Combining all of these components of $\nabla_\lambda \mathcal{L}$ into a single vector and using the definition of $\lambda$ in \eqref{eq:definition_of_mu_alg} yields
	\begin{equation*}
		\nabla_\lambda \mathcal{L}(w, \lambda) = e - \alpha \mathbf{1} + S \lambda = e - \alpha \mathbf{1} + S \left(-S^{-1}\left(e - \alpha \mathbf{1}\right)\right) = 0.
	\end{equation*}

	Taking the directional derivative of $\mathcal{L}$ with respect to $w$ in direction $h$ and using \eqref{eq:inline_wi_lemma} yields
	\begin{align*}
		\nabla_w \mathcal{L}(w, \lambda)h &= \left(\Delta w, \Delta h\right)_{L^2(\Omega)} - \sum_{j=1}^r \lambda_j h(x_j) \\
		&= \left(\Delta w, \Delta h\right)_{L^2(\Omega)} - \sum_{j=1}^r \lambda_j \left(\psi_j, \Delta h\right)_{L^2(\Omega)} \\
		&= \left(\Delta w - \sum_{j=1}^r \lambda_j \psi_j,~ \Delta h\right)_{L^2(\Omega)}.
	\end{align*}
	Using the definition of $w$ in Algorithm \ref{alg:weighting_functions_incremental}, and the fact that the Laplacian of a constant function is zero, we have
	\begin{align*}
		\Delta w &= -\sum_{j=1}^r \lambda_j \Delta \theta_j \\
		&= -\sum_{j=1}^r \lambda_j \psi_j
	\end{align*}
